Environmental and geographic variables are effective surrogates for genetic variation in conservation planning

### 2017-11-22 code/rmarkdown/article.Rmd
fix citations

Here we determine whether environmental and geographic surrogates capture adaptive and neutral genetic variation respectively in the context of conservation planning. We use distribution and genomic data for 27 alpine plant species in the European Alps that was obtained by the IntraBioDiv project ([@r451]). The data were collected following a gridded sampling scheme which we adopted as planning units for this study. We show that for most species the spatial patterns of adaptive and neutral genetic variation correlated with environmental (obtained from WorldClim; [@r33]) and geographic variables. We also show that for most species the level of association is strong enough to be operational for conservation planning. Finally, we demonstrate that using these surrogates results in prioritizations that secure a substantial proportion of intra-specific genetic variation.

@@

We used data for 27 alpine plant species in the European Alps collected by the IntraBioDiv project ([@r451]; Fig. 3a). This data set has been used to explore patterns of adaptive (e.g. [@r455]) and neutral genetic variation (e.g. [@r478]), and the potential for species richness as a surrogate for genetic diversity ([@r486]). Data were collected using a $20^{\prime}$ longitude by $12^{\prime}$ latitude grid (approx. 20 $\times$ 22.5 km; Fig. S31). Project surveyors visited every second grid cell, and for each species, they collected samples from three individuals if any individuals were found. They genotyped samples using AFLPs, and constructed matrices denoting the presence of polymorphisms at loci for each species (mean `r round(mean(sapply(spp.StructureData.LST, structurer:::n.loci)),2)` $\pm$ `r round(sd(sapply(spp.StructureData.LST, structurer:::n.loci)),1)` SD markers genotyped per species; for more information see [@r478]). Thus the data set contains information describing the genomic properties of individuals for each species over a geographic grid. We used these data because they comprised comparable genetic information for a range of species with different evolutionary and life histories collected using a standardized sampling scheme. To permit replication and validation of this study, all of our data, code, and results are stored in an online repository (\url{www.github.com/jeffreyhanson/genetic-surrogates}) and are also available under the digital object identifier (DOI) \texttt{10.5281/zenodo.843625}. All spatial and statistical analyses were conducted in \texttt{R} (version `r paste0(R.version$major, '.', R.version$minor)`; [@r192]).

>>>>

Here we determine whether environmental and geographic surrogates capture adaptive and neutral genetic variation respectively in the context of conservation planning. We use distribution and genomic data for 27 alpine plant species in the European Alps that was obtained by the IntraBioDiv project ([@r486]). The data were collected following a gridded sampling scheme which we adopted as planning units for this study. We show that for most species the spatial patterns of adaptive and neutral genetic variation correlated with environmental (obtained from WorldClim; [@r33]) and geographic variables. We also show that for most species the level of association is strong enough to be operational for conservation planning. Finally, we demonstrate that using these surrogates results in prioritizations that secure a substantial proportion of intra-specific genetic variation.

@@

We used data for 27 alpine plant species in the European Alps collected by the IntraBioDiv project ([@r486]; Fig. 3a). This data set has been used to explore patterns of adaptive (e.g. [@r455]) and neutral genetic variation (e.g. [@r478]), and the potential for species richness as a surrogate for genetic diversity ([@r486]). Data were collected using a $20^{\prime}$ longitude by $12^{\prime}$ latitude grid (approx. 20 $\times$ 22.5 km; Fig. S31). Project surveyors visited every second grid cell, and for each species, they collected samples from three individuals if any individuals were found. They genotyped samples using AFLPs, and constructed matrices denoting the presence of polymorphisms at loci for each species (mean `r round(mean(sapply(spp.StructureData.LST, structurer:::n.loci)),2)` $\pm$ `r round(sd(sapply(spp.StructureData.LST, structurer:::n.loci)),1)` SD markers genotyped per species; for more information see [@r478]). Thus the data set contains information describing the genomic properties of individuals for each species over a geographic grid. We used these data because they comprised comparable genetic information for a range of species with different evolutionary and life histories collected using a standardized sampling scheme. To permit replication and validation of this study, all of our data, code, and results are stored in an online repository (\url{www.github.com/jeffreyhanson/genetic-surrogates}) and are also available under the digital object identifier (DOI) \texttt{10.5281/zenodo.843625}. All spatial and statistical analyses were conducted in \texttt{R} (version `r paste0(R.version$major, '.', R.version$minor)`; [@r192]).
